\documentclass[oneside,10pt]{amsart}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{graphics,graphicx}
\usepackage{verbatim}
%\RequirePackage[usenames]{color}
\usepackage{color}
\usepackage{multicol}
%\usepackage{fullpage}

\usepackage[left=1in,top=0.8in,right=1in,bottom=1in]{geometry}


%{\footnotesize\newline{\color{red}\fbox{\parbox{\textwidth-15pt}{\textbf{todo: } #1}}}\newline}}

\renewcommand{\O}{\mathcal O}
%\DeclareMathOperator{\Spec}{{Spec}}
%\newcommand{\bQ}{\mathbb{Q}}
\title{Syllabus -- Math 5320, Section \#1}
\author{Introduction to Modern Algebra II}

\begin{document}
\maketitle

\noindent
{\bf Description: } This is a course on rings, fields and modules.  We in particular aim to study modules over PIDs and Euclidean domains and also Galois theory.
\vskip 12pt

\begin{itemize}
 \item{} {\bf Time:  }  Monday, Wednesday, Friday 12:55 PM -- 1:45 PM.
 \item{} {\bf Location:  }   AEB 310.
 \item{} {\bf Instructor: }  Karl Schwede
\item{}  {\bf Contact information:}
\begin{itemize}
 \item{}  {email: }  schwede@math.utah.edu
 \item{}  {office:  } JWB 315
 \item{}  {website: }  {\tt{http://www.math.utah.edu/{\textasciitilde}schwede/math5320}} \hskip 12pt
 (or see Canvas). 
\end{itemize}
\item{}  {\bf Office hours:}  TBD
\end{itemize}

\begin{itemize}
 \item{} {\bf Textbook: }
 {\it Algebra, 2nd edition} by Michael Artin.
\end{itemize}
\vskip 12pt
%\hskip -12pt
 {\bf Grade:}  Your grade will be determined by the following formula.
\begin{itemize}
\item[15\%]  Homework and in-class group worksheets  Worksheets will be once every 1-2 weeks.  There will be periodic individual homework.  
\item[20\%]  Quizzes will once every 1 or 2 weeks.  Your lowest quiz score will be dropped.
\item[15\%]  Midterm \#1.  Tentatively Monday, February 10th.
\item[20\%]  Midterm \#2.  Tentatively Monday, March 16th.
\item[30\%]  Final.  Scheduled as per University guidelines.
\end{itemize}
In terms of letter grade assignments, here is the minimum scale (the final scale may be more generous than what is written here).  
\begin{multicols}{4}
\begin{itemize}
\item[93+] will be an A,
\item[90-92] will be an A-,
\item[87-89] will be a B+,
\item[83-86] will be a B,
\item[80-82] will be a B-,
\item[77-79] will be a C+,
\item[73-76] will be a C,
\item[70-72] will be a C-,
\item[67-69] will be a D+,
\item[63-66] will be a D,
\item[60-62] will be a D-,
\item[0-59] will be an E.
\end{itemize}
\end{multicols}
Generally speaking, late homework will not be accepted without permission first.  You must speak with the instructor \emph{prior} to missing the homework in order to receive credit.  In such situations, the impact on the grade will be dealt with on a case by case basis.  

\begin{itemize}
    \item{} We will try using {\tt gradescope} to both turn in and grade homework, worksheets etc.
\end{itemize}

Students are allowed, and even encouraged to work together when solving homework problems (although each student is responsible for their own write-up, unless it is specifically a group assignment).
\vskip 8pt
\hskip -12pt
{\bf Prerequisites: }  They officially are ``C" or better in Math 5310.
\vskip 8pt
\hskip -12pt
{\bf Academic Integrity: } All University of Utah policies regarding ethics and honorable behavior apply to
this course.
\vskip 8pt
\hskip -12pt
{\bf Disabilities: } The Americans with Disabilities Act requires that reasonable accommodations be provided to qualified individuals. To discuss any such accommodations, please contact me as well as the Center for Disability Services, (801) 581-5020, at the beginning of the semester.
\vskip 8pt
\noindent
{\bf Safety:}  The University of Utah values the safety of all campus community members. To report suspicious activity or to request a courtesy escort, call campus police at 801-585-COPS (2677). You will receive important emergency alerts and safety messages regarding campus safety via text message. For more information regarding safety and to view available training resources, including helpful videos, visit safeu.utah.edu.
\end{document}
